New strategies for multi-factoral and temporal behavioral analyses

### 2019-06-16 docs/main.tex
version 2

\begin{block}{{\normalsize Deteremine the extent of correlation in gene expression variation}}

@@

\begin{block}{Preliminary interpreations}

@@

\begin{itemize}
\item \textbf{Zoom out:} examine the full model of sex * tissue * treatment. 
\item \textbf{Zoom in:} examine effects of specific manipulations in greater detail. 
\item \textbf{Create} and open source R package that can be peer reviewed. 
\item \textbf{Share} tutorials for how to use the function. 
\end{itemize}

>>>>

\begin{block}{{\normalsize Determine the extent of correlation in gene expression variation}}

@@

\begin{block}{Preliminary interpretations}

@@

\begin{itemize}
\item \textbf{Zoom out:} examine the full model of sex * tissue * treatment. 
\item \textbf{Zoom in:} examine effects of specific manipulations in greater detail. 
\item \textbf{Test} specific hypotheses. 
\item \textbf{Incorporate} code-review and peer-review . 
\item \textbf{Create} and open source R package. 
\item \textbf{Share} tutorials for how to use the function. 
\end{itemize}
